% TODO: How can autonomous robots be used 
% TODO: Refer to related work
%         - Nature
%         - AI
%         - Behavioral algorithms for grass cutting
%         - Search and rescue?
% TODO: Reflections (what is yet to be done?)

% The concept of multiple entities collaborating to achieve a common goal is well-established. Nature offers numerous examples, where diverse species of animals and plants have co-evolved to enhance mutual survival.
% Ants, despite possessing only rudimentary communication methods, represent one of the most successful animal species. They communicate and work together effectively using chemical signals.

% A paper review by Janardan Kumar Verma \& Virender Ranga outlines the current state MRS and provides a taxonomy for describing types of MRS and the problems and solutions related to them. This article mentions several approaches solving the task assignment problem. Notable approaches include market-based, dynamic programming, optimisation based, behavior based and deep reinforcement learning. Market based task assignment involves an auction where robots bid on a task and the highest bidding robot gets assigned the task which results in nearly optimal task assignment. Dynamic programming approaches seek to calculate the optimal task assignment given the location and capabilities of all robots in the system. This usually requires information about the entire MRS to be solved and can therefore only be used in centralized approaches.

% A whole other approach is deep reinforcement learning. Here, the MRS learns to reduce cost function and find the optimal policy for selecting tasks. Advantages include being adaptive to any environment at the cost of extensive training.

% TODO: We say the same applications in "Introduction". Is this bad??
\section{Related Work}
Multi-Robot Systems (MRS) represent a well-established field within robotics, with applications spanning search and rescue, environmental monitoring, warehouse automation, exploration, and surveillance. 
MRS architectures are generally categorized as either centralized or distributed. 
In centralized approaches, a central server is responsible for assigning tasks and planning paths for all robots in the system. 
In contrast, distributed algorithms enable each robot to perform local planning and decision-making, often based on partial knowledge and limited communication.\\

Notable approaches to MRS control include market-based methods~\cite{trigui2014market}, dynamic programming~\cite{kato2011dp}, optimization-based methods, behavior-based strategies, and deep reinforcement learning~\cite{huttenrauch2019deep-swarm}. In market-based task assignment, robots participate in an auction by bidding for tasks, with the highest bidder receiving the assignment. This method can lead to near-optimal task distributions, especially when task costs are well-defined. Dynamic programming approaches aim to compute optimal task allocations and trajectories based on the known locations and capabilities of all robots. These methods typically require complete, up-to-date global information and are thus most suitable for centralized systems, or for distributed systems in which the full system state is shared \cite{multi-robot-search-moving-target}.
Behavior-based approaches often draw inspiration from biological systems, such as ants and bees, and use indirect coordination methods like virtual “pheromones” or other spatial markers to guide robot behavior. One paper found that “a coordinated group effort is possible without use of direct communication or robot differentiation” \cite{kube2000cooperative-ants}. Such strategies reduce the reliance on explicit communication and instead emphasize emergent, self-organizing behaviors. \\

This project adopts a similar approach by enabling robots to share a continuous stream of observations over a communication channel. These collective observations are used to update each robot’s internal representation of the search map, which in turn influences its navigation decisions. This form of implicit communication allows for scalable coordination, as the time complexity of the algorithm does not increase with the number of participating robots \cite{multi-robot-search-moving-target}.\\

Four algorithmic approaches are explored in this work: a lightweight gradient-based method, a frontier exploration algorithm using A* for path planning, a hybrid strategy combining the two, and a deep reinforcement learning-based algorithm. 
While these methods may not always produce optimal exploration strategies, they are designed to be robust, computationally efficient, and adaptable to a variety of real-world scenarios.
